% This must be in the first 5 lines to tell arXiv to use pdfLaTeX, which is strongly recommended.
\pdfoutput=1
% In particular, the hyperref package requires pdfLaTeX in order to break URLs across lines.

\documentclass[11pt]{article}

\usepackage[review]{acl}

% Standard package includes
\usepackage{times}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{booktabs}

% For proper rendering and hyphenation of words containing Latin characters (including in bib files)
\usepackage[T1]{fontenc}
% For Vietnamese characters
% \usepackage[T5]{fontenc}
% See https://www.latex-project.org/help/documentation/encguide.pdf for other character sets

% This assumes your files are encoded as UTF8
\usepackage[utf8]{inputenc}

% This is not strictly necessary, and may be commented out.
% However, it will improve the layout of the manuscript,
% and will typically save some space.
\usepackage{microtype}

% This is also not strictly necessary, and may be commented out.
% However, it will improve the aesthetics of text in
% the typewriter font.
\usepackage{inconsolata}


% If the title and author information does not fit in the area allocated, uncomment the following
%
%\setlength\titlebox{<dim>}
%
% and set <dim> to something 5cm or larger.

\title{CSC401 Homework Assignment \#2\\Analysis}

\author{Yuwei (Johnny) Meng \\
  Student number: \texttt{1007824810} \\
  UTORid: \texttt{mengyuwe} \\
  \texttt{johnny.meng@mail.utoronto.ca}}

\begin{document}
\maketitle

\section{Training Results}

\subsection{Training Loop Printout}

\paragraph{Model with Pre-layer Normalization}
\begin{small}
\begin{verbatim}
  [Device:cuda] Epoch 1 Training ====
  Epoch: 100% 2171/2171 [01:56<00:00, 18.69it/s]
  [Device:cuda] Epoch 1 Validation ====
  Epoch 1: loss=6.246624596598839, BLEU-4: 15.9045 BLEU-3: 18.9850, time=00:02:32
  [Device:cuda] Epoch 2 Training ====
  Epoch: 100% 2171/2171 [01:58<00:00, 18.30it/s]
  [Device:cuda] Epoch 2 Validation ====
  Epoch 2: loss=2.6125431804819517, BLEU-4: 32.3820 BLEU-3: 38.9379, time=00:05:00
  [Device:cuda] Epoch 3 Training ====
  Epoch: 100% 2171/2171 [01:58<00:00, 18.29it/s]
  [Device:cuda] Epoch 3 Validation ====
  Epoch 3: loss=1.8071209433330253, BLEU-4: 34.4108 BLEU-3: 41.2555, time=00:07:29
  [Device:cuda] Epoch 4 Training ====
  Epoch: 100% 2171/2171 [01:58<00:00, 18.27it/s]
  [Device:cuda] Epoch 4 Validation ====
  Epoch 4: loss=1.4453762439141786, BLEU-4: 35.5304 BLEU-3: 42.1599, time=00:09:56
  [Device:cuda] Epoch 5 Training ====
  Epoch: 100% 2171/2171 [01:58<00:00, 18.40it/s]
  [Device:cuda] Epoch 5 Validation ====
  Epoch 5: loss=1.1869039849332268, BLEU-4: 36.1735 BLEU-3: 42.8110, time=00:12:23
  [Device:cuda] Epoch 6 Training ====
  Epoch: 100% 2171/2171 [01:58<00:00, 18.36it/s]
  [Device:cuda] Epoch 6 Validation ====
  Epoch 6: loss=0.9999292358611928, BLEU-4: 36.3233 BLEU-3: 42.9580, time=00:14:53
  [Device:cuda] Epoch 7 Training ====
  Epoch: 100% 2171/2171 [01:58<00:00, 18.38it/s]
  [Device:cuda] Epoch 7 Validation ====
  Epoch 7: loss=0.8557376364638102, BLEU-4: 36.7024 BLEU-3: 43.2409, time=00:17:22
  Finished 7 epochs
\end{verbatim}
\end{small}

\vspace{2em}

\subsection{Test Set BLEU Score}

\begin{table}[h]
\centering
\begin{tabular}{lcc} \toprule
Model                          & BLEU-4 &  BLEU-3 \\ \midrule
Model Pre-layer Normalization  & 41.9362 & 48.9238 \\
\bottomrule
\end{tabular}
\caption{The BLEU score reported on the test set for the pre-layer model.}
\label{tab:bleu}
\end{table}

\section{Translation Analysis}

\subsection{Translations}

\begin{enumerate}
  \item Voila des mesures qui favorisent la famille canadienne.
  \begin{enumerate}
    \item \textbf{My Model:} these measures promote canadian family
    \item \textbf{Bart:} These are measures that favour the Canadian family.
    \item \textbf{Google Translate:} These are measures that favor the Canadian family.
  \end{enumerate}
  \item Je voudrais aussi signaler aux deputes qu'ils peuvent maintenant s'avancer pour voter.
  \begin{enumerate}
    \item \textbf{My Model:} i would also like to point out that they can move to vote
    \item \textbf{Bart:} I also want to tell members that they can now vote.
    \item \textbf{Google Translate:} I would also like to point out to members that they can now come forward to vote.
  \end{enumerate}
  \item Trudeau embauche un cabinet de consultants pour examiner la dependance excessive du gouvernement a l'egard des cabinets de consultants.
  \begin{enumerate}
    \item \textbf{My Model:} trudeau s office to review consultants look at the government s excessive dependency
    \item \textbf{Bart:} Trudeau is creating a consulting cabinet to look at the excessive dependence of the government on
    \item \textbf{Google Translate:} Trudeau hires consulting firm to examine government's overreliance on consulting firms.
  \end{enumerate}
  \item Pierre demande s'il vous plait s'il peut s'attribuer le merite d'avoir supprime 600 emplois a la SRC.
  \begin{enumerate}
    \item \textbf{My Model:} pierre s please take the credit
    \item \textbf{Bart:} Pierre asks if you would support the merit of removing 600 jobs from the RCMP.
    \item \textbf{Google Translate:} Pierre please asks if he can take credit for cutting 600 jobs at the SRC.
  \end{enumerate}
  \item La France a remporte la coupe du monde 2018.
  \begin{enumerate}
    \item \textbf{My Model:} france has won the world s cuts
    \item \textbf{Bart:} France won the world in 2018.
    \item \textbf{Google Translate:} France won the 2018 World Cup.
  \end{enumerate}
  \item J'avais a peine de l'eau a boire pour huit jours.
  \begin{enumerate}
    \item \textbf{My Model:} i barely had a drink for eight days
    \item \textbf{Bart:} I had enough water for eight days.
    \item \textbf{Google Translate:} I barely had water to drink for eight days.
  \end{enumerate}
  \item Toronto est une ville du Canada.
  \begin{enumerate}
    \item \textbf{My Model:} toronto is a city of canada
    \item \textbf{Bart:} Toronto is a city of Canada.
    \item \textbf{Google Translate:} Toronto is a city in Canada.
  \end{enumerate}
  \item Les etudiants de l'Universite de Toronto sont excellents.
  \begin{enumerate}
    \item \textbf{My Model:} the university of toronto is excellent
    \item \textbf{Bart:} The students at the University of Toronto are excellent.
    \item \textbf{Google Translate:} The students at the University of Toronto are excellent.
  \end{enumerate}
\end{enumerate}

\subsection{Discussion}
{\it In this section, write a brief discussion on your findings. Describe the quality of
those sentences. How's your model compared with Google Translate or ChatGPT?}

\end{document}
